The Rapid Cycleway Prioritisation Tool

### 2020-06-15 rapid-slides.Rmd
Tweak slides

@@

>>>>

```{r, engine='bash', eval=FALSE, echo=FALSE}
cp rapid-slides.html popupCycleways/v1/slides/index.html
cp -Rv libs popupCycleways/v1/slides/
cd popupCycleways
git status
git add -A
git commit -am 'Add slides'
git push
cd -
```

```{r, eval=FALSE, echo=FALSE}
# Aim: make pdf slides
pagedown::chrome_print("rapid-slides.html")
browseURL("rapid-slides.pdf")
piggyback::pb_upload("rapid-slides.pdf")
piggyback::pb_download_url("rapid-slides.pdf")
```

@@

<!-- Tweet: @ launch -->

<!-- The Rapid Cycleway Prioritisation Tool is finally launched 🚀 -->

<!-- It provides evidence to support road space reallocation for active travel in response to #COVID19. -->

<!-- Article: -->
<!-- Preprint of methods: -->
<!-- Web tool (free and #opensource):  -->
